### 2019-05-22 5_evaluation.tex
Add weak/strong scaling figures.
Add GPU efficiency figure.
Fiddle with figure placement, labels, listing font size.
Fiddle with figure placement.
New section to describe weak and strong scaling curves.

@@

@@

\input{e1_flops}
\input{e2_efficiency}

@@

\input{e7_bytes}
\input{e4_radix}

@@

Spark, Swift/T and TensorFlow
are omitted from comparisons with more complicated dependencies, as the higher overheads of these systems would have required
unreasonably large problem sizes (beyond what can be completed in 6
hours) to reach 50\% efficiency. Regent and X10 are incomplete as Cori was highly impacted before the deadline; complete results will be in the final paper.

@@

@@

@@

\input{e5_imbalance}

@@

\input{e6_communication}

@@

>>>>

For GPU experiments we use the Piz Daint supercomputer~\cite{PizDaint}, a Cray XC50 with
one Intel Xeon E5-2690 v3 (12 physical cores) and one NVIDIA Tesla
P100 per node. We use GCC \textbf{X.Y}, Cray MPICH \textbf{Z.W}, and
CUDA \textbf{A.B}.

% FIXME: get Piz Daint software versions.

@@

\input{e1_flops}
\input{e2_efficiency}
\input{e7_bytes}
\input{e4_radix}

@@

@@

@@

Spark, Swift/T and TensorFlow
are omitted from comparisons with more complicated dependencies, as the higher overheads of these systems would have required
unreasonably large problem sizes (beyond what can be completed in 6
hours) to reach 50\% efficiency.

@@

\input{e8_weak}
\input{e9_strong}

@@

\subsection{Comparison with Weak and Strong Scaling}

Figures~\ref{fig:weak-scaling} and \ref{fig:strong-scaling} show
conventional strong and weak scaling of the stencil pattern for
comparison with the METG results in
Figure~\ref{fig:metg-compute-stencil}. At small node counts, where the
average task granularity is larger than the METG for most systems, the
performance is ideal. For several systems METG rises with node count,
and this becomes visible in the weak and strong scaling graphs as
non-ideal performance. Thus the shape of the weak and strong scaling
graphs effectively interpolates between ideal performance and the METG
curve depending on how close each system is to being limited by
overhead.

@@

\input{e5_imbalance}
\input{e6_communication}

@@

@@

\subsection{Heterogeneous Processors}

\input{e10_cuda_efficiency}

% FIXME: TODO
